A comparison between the latest Prophet forecasting model and the ARIMA model: An evaluation of BTC/ZAR predictability

### 2017-11-06 Draft/Write-up/Draft.Rmd
Definitely Final Paper

Prophet, like the GAM, frames the forecasting problem as a curve fitting exercise and uses backfitting to find the regression functions. This allows for the model to be fitted quickly and missing values and large outliers to be handled elegantly. The regression model also provides model flexibility and allows the analyst to interactively change model parameters [@taylor2017]. 
The growth component of Prophet may be modelled as a linear or non-linear function of time. Linear growth is modelled by a piecewise constant function while non-linear growth is modelled similar to population growths which use a logistic growth model [@taylor2017]. A time-varying upper limit may be specified for logistic growth, at which point the forecasts will saturate. This carrying capacity allows the analyst to incorporate their prior knowledge about the maximum obtainable growth level such as the total market or population size into the model. Prophet accounts for changes in the trajectory of this trend by automatically detecting and selecting changepoints in the data at which the growth rate is allowed to change. These changepoints have a Laplace prior distribution placed on them and its scale parameter may be used to adjust the flexibility of the trend and to choose how aggressively the model should follow historical trend changes. Analysts may also adjust the number of potential changepoints included or manually specify their location. This allows non-experts with knowledge about events that may affect the growth rate to use the parameter as a knob to either increase or decrease the number of changepoints included [@taylor2017]. It also allows for the analyst to add changepoints which the automatic selection procedure may have missed or remove changepoints when the model is overfitting historical trends [@taylor2017].

@@

Prophet’s ability to forecast at scale enables it to model a wide variety of data and may be able to adequately fit exchange rate data. Its non-linear components could capture the non-linearity present in exchange rates. In contrast, the ARIMA model is a linear function of previous observations and lagged residuals and fails to capture the non-linearity inherent in exchange rate data. Prophet performs well on data with strong multiple “human scale” seasonalities and historical trend changes. This differs to the ARIMA model which requires the data to be de-trended and the variance stabilised before the model can be fitted. Hence Prophet could model the weekly seasonality of closing prices due to low trading activity which occurs around the weekend and high trading activity which occurs mid-week.

@@

# Methodology \label{Methodology}
In this paper, the out-of-sample forecasts of ARIMA and Prophet are compared over varying forecast horizons. The data is first split into a training set and test set. The training set starts on the 24th January 2016 and ends on the 16th January 2017, while the test set starts on the 17th January 2017 and ends on the 17th July 2017. The Box-Jenkins methodology is then used to select the correct ARIMA model while Prophet’s semi-automatic procedure is used for model selection. The selected ARIMA and Prophet model are then fitted to the training set and rolling window forecasts are made 1 day, 30 days and 90 days ahead. This allows us to examine the forecast horizon effect. The Model Confidence Set and Mincer-Zarnowitz test is then used to evaluate the forecasts produced by ARIMA and Prophet against the test set. Since there is no consensus on which accuracy statistic best measures the performance of forecasting techniques, the most popular criteria, the Root Mean Squared Error (RMSE) is employed. The results obtained from the ARIMA model will be used as a benchmark for comparison. This process is then repeated based on data which has outliers and missing values present.

@@

This paper makes use of Prophet’s default settings to fit the data, however weekly seasonality is included in the model. This allows us to account for our prior knowledge about the closing prices of Bitcoin which tend to be lower around the weekend however higher mid-week due to fluctuations in trading activity. Furthermore, a linear trend is appropriate since Bitcoin does not have an upper limit on its closing prices.

## Rolling Window Forecasts
Rolling window forecasts are useful in evaluating the robustness of a forecasting method. In a rolling window forecast, the forecasts are made h-steps at a time and the actual observation rather than the predicted value is used for the next prediction in the forecast horizon. In this way, a poor forecast will not have negative consequences on future forecasts to be made since the observed values will be used to correct itself for the remaining forecasts [@zhang1998]. In this paper, the ARIMA and Prophet model is first fitted to the training set and the returns are forecasted h-days ahead for h = 1, 30, 90. The size of the training set is then increased by one observation and the models are refitted. The next h-day ahead return is forecasted and this process is repeated until all forecasts have been made into the test set. The h-day ahead forecasts are then compared to the h-day ahead observed values in the test set and the forecast errors are calculated to determine the RMSE.

@@

$$e_R = \arg max_{i}\bigg(\sup_{j\in M}\frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\bigg)$$
## Mincer-Zarnowitz Approach to Forecast Evaluation 
The Mincer-Zarnowitz approach to evaluating forecast accuracy is commonly used and can be useful when comparing the forecasts produced by Prophet and the ARIMA model. @mincer1969 proposed an absolute measure to evaluate forecast accuracy that considers the distance between the actual and predicted values. To analyse the absolute errors produced by the forecasts, the observed values $r_t$ are regressed against the predicted values $\hat{r_t}$, i.e. 
$$r_t = \alpha + \beta\cdot\hat{r_t} + e_t$$
where $\alpha$ represents the mean distance between the observed and predicted values while $\beta$ represents the correlation between the forecasted errors and predicted values. When $\alpha = 0$ it implies that the forecasts are unbiased and do not systematically overestimate or underestimate the data. When $\beta = 1$ it implies that the forecasts are efficient and uncorrelated with the forecasted errors. A joint hypothesis test of $H_0: \alpha = 0 \cup \beta = 1$ is performed to check the efficiency and bias of the forecasts and the model which produces the best results generates superior forecasts.

>>>>

Prophet, like the GAM, frames the forecasting problem as a curve-fitting exercise and uses backfitting to find the regression functions. This allows for the model to be fitted quickly and missing values and large outliers to be handled elegantly. The regression model also provides model flexibility and allows the analyst to interactively change model parameters [@taylor2017]. 
The growth component of Prophet may be modelled as a linear or non-linear function of time. Linear growth is modelled by a piecewise constant function while non-linear growth is modelled similar to population growths which use a logistic growth model [@taylor2017]. A time-varying upper limit may be specified for logistic growth, at which point the forecasts will saturate. This carrying capacity allows the analyst to incorporate their prior knowledge about the maximum obtainable growth level such as the total market or population size into the model. Prophet accounts for changes in the trajectory of this trend by automatically detecting and selecting changepoints in the data at which the growth rate is allowed to change. These changepoints have a Laplace prior distribution placed on them and its scale parameter may be used to adjust the flexibility of the trend and to choose how aggressively the model should follow historical trend changes. Analysts may also adjust the number of potential changepoints included or manually specify their location. This allows non-experts with knowledge about events that may affect the growth rate to use the parameter as a knob to either increase or decrease the number of changepoints included [@taylor2017]. It also allows for the analyst to add changepoints which the automatic selection procedure may have missed or remove changepoints when the model is overfitting historical trends [@taylor2017].

@@

Prophet's ability to forecast at scale enables it to model a wide variety of data and may be able to adequately fit exchange rate data. Its non-linear components could capture the non-linearity present in exchange rates. In contrast, the ARIMA model is a linear function of previous observations and lagged residuals and fails to capture the non-linearity inherent in exchange rate data. Prophet performs well on data with strong multiple "human scale" seasonalities and historical trend changes. This differs to the ARIMA model which requires the data to be de-trended and the variance stabilised before the model can be fitted. Hence Prophet could model the weekly seasonality of closing prices due to low trading activity which occurs around the weekend and high trading activity which occurs mid-week.

@@

# Methodology \label{Methodology}
In this paper, the out-of-sample forecasts of ARIMA and Prophet are compared over varying forecast horizons. The data is first split into a training set and test set. The training set starts on the 24th January 2016 and ends on the 16th January 2017, while the test set starts on the 17th January 2017 and ends on the 17th July 2017. The Box-Jenkins methodology is then used to select the correct ARIMA model while Prophet's semi-automatic procedure is used for model selection. The selected ARIMA and Prophet model are then fitted to the training set and rolling window forecasts are made 1 day, 30 days and 90 days ahead. This allows us to examine the forecast horizon effect. The Model Confidence Set and Mincer-Zarnowitz test is then used to evaluate the forecasts produced by ARIMA and Prophet against the test set. Since there is no consensus on which accuracy statistic best measures the performance of forecasting techniques, the most popular criteria, the Root Mean Squared Error (RMSE) is employed. The results obtained from the ARIMA model will be used as a benchmark for comparison. This process is then repeated based on data which has outliers and missing values present.

@@

This paper makes use of Prophet's default settings to fit the data, however weekly seasonality is included in the model. This allows us to account for our prior knowledge about the closing prices of Bitcoin which tend to be lower around the weekend however higher mid-week due to fluctuations in trading activity. Furthermore, a linear trend is appropriate since Bitcoin does not have an upper limit on its closing prices.

## Rolling Window Forecasts
Rolling window forecasts are useful in evaluating the robustness of a forecasting method. In a rolling window forecast, the forecasts are made h-steps at a time and the actual observation rather than the predicted value is used for the next prediction in the forecast horizon. In this way, a poor forecast will not have negative consequences on future forecasts to be made since the observed values will be used to correct itself for the remaining forecasts [@zhang1998]. In this paper, the ARIMA and Prophet models are first fitted to the training set and the returns are forecasted h-days ahead for h = 1, 30, 90. The size of the training set is then increased by one observation and the models are refitted. The next h-day ahead return is forecasted and this process is repeated until all forecasts have been made into the test set. The h-day ahead forecasts are then compared to the h-day ahead observed values in the test set and the forecast errors are calculated to determine the RMSE.

@@

$$e_R = \arg max_{i}\bigg(\sup_{j\in M}\frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\bigg)$$

## Mincer-Zarnowitz Approach to Forecast Evaluation 
The Mincer-Zarnowitz approach to evaluating forecast accuracy is commonly used and can be useful when comparing the forecasts produced by Prophet and the ARIMA model. @mincer1969 proposed an absolute measure to evaluate forecast accuracy that considers the distance between the actual and predicted values. To analyse the absolute errors produced by the forecasts, the observed values $r_t$ are regressed against the predicted values $\hat{r_t}$, i.e. 
$$r_t = \alpha + \beta\cdot\hat{r_t} + e_t$$
where $\alpha$ represents the mean distance between the observed and predicted values while $\beta$ represents the correlation between the forecasted errors and predicted values. When $\alpha = 0$ it implies that the forecasts are unbiased and do not systematically overestimate or underestimate the data. When $\beta = 1$ it implies that the forecasts are efficient and uncorrelated with the forecasted errors. A joint hypothesis test of $H_0: \alpha = 0 \cup \beta = 1$ is performed to check the efficiency and bias of the forecasts and the model which produces the best results generates superior forecasts.

### 2017-11-06 Draft/Write-up/Draft.tex
Definitely Final Paper

The techniques that have been considered for exchange rate forecasting
thus far, require the analyst to have vocational knowledge about time
series. Prophet differs from traditional time series models in that it
is flexible and can be customised by a large number of non-experts who
have little knowledge about time series, however have domain knowledge
about the data generating process. Prophet allows for a large number of
forecasts to be produced across a variety of problems and consists of a
robust evaluation system that allows for a large number of forecasts be
evaluated and compared. This is Facebookâs definition of forecasting
at scale.

Prophetâs Bayesian approach to forecasting allows the analyst to
incorporate their expert knowledge into the model building process and
has produced significantly improved forecasts compared to the ARIMA
model. Taylor and Letham (2017) forecasted the number of events on
Facebook using Prophet. The time series was impacted by holidays, had
strong multi-period seasonality, and a piecewise trend. The forecasts
produced by Prophet were compared to common forecasting techniques such
as exponential smoothing, ARIMA, the seasonal naive, and the naive
model. While exponential smoothing and the seasonal naive model were
quite robust, the ARIMA forecasts were fragile. No model besides Prophet
accounted for the dips around holidays and the upward trend of the time
series towards later observations. If Prophet produces forecasts that
are as good as the ARIMA model when forecasting BTC/ZAR, it can be
compared to more complex forecasting methods that are less tractable
such as the hybrid models and machine learning techniques seen earlier.

@@

Prophet, like the GAM, frames the forecasting problem as a curve fitting
exercise and uses backfitting to find the regression functions. This
allows for the model to be fitted quickly and missing values and large
outliers to be handled elegantly. The regression model also provides
model flexibility and allows the analyst to interactively change model
parameters (Taylor and Letham 2017). The growth component of Prophet may
be modelled as a linear or non-linear function of time. Linear growth is
modelled by a piecewise constant function while non-linear growth is
modelled similar to population growths which use a logistic growth model
(Taylor and Letham 2017). A time-varying upper limit may be specified
for logistic growth, at which point the forecasts will saturate. This
carrying capacity allows the analyst to incorporate their prior
knowledge about the maximum obtainable growth level such as the total
market or population size into the model. Prophet accounts for changes
in the trajectory of this trend by automatically detecting and selecting
changepoints in the data at which the growth rate is allowed to change.
These changepoints have a Laplace prior distribution placed on them and
its scale parameter may be used to adjust the flexibility of the trend
and to choose how aggressively the model should follow historical trend
changes. Analysts may also adjust the number of potential changepoints
included or manually specify their location. This allows non-experts
with knowledge about events that may affect the growth rate to use the
parameter as a knob to either increase or decrease the number of
changepoints included (Taylor and Letham 2017). It also allows for the
analyst to add changepoints which the automatic selection procedure may
have missed or remove changepoints when the model is overfitting
historical trends (Taylor and Letham 2017).

@@

Prophetâs ability to forecast at scale enables it to model a wide
variety of data and may be able to adequately fit exchange rate data.
Its non-linear components could capture the non-linearity present in
exchange rates. In contrast, the ARIMA model is a linear function of
previous observations and lagged residuals and fails to capture the
non-linearity inherent in exchange rate data. Prophet performs well on
data with strong multiple âhuman scaleâ seasonalities and historical
trend changes. This differs to the ARIMA model which requires the data
to be de-trended and the variance stabilised before the model can be
fitted. Hence Prophet could model the weekly seasonality of closing
prices due to low trading activity which occurs around the weekend and
high trading activity which occurs mid-week.

@@

In this paper, the out-of-sample forecasts of ARIMA and Prophet are
compared over varying forecast horizons. The data is first split into a
training set and test set. The training set starts on the 24th January
2016 and ends on the 16th January 2017, while the test set starts on the
17th January 2017 and ends on the 17th July 2017. The Box-Jenkins
methodology is then used to select the correct ARIMA model while
Prophetâs semi-automatic procedure is used for model selection. The
selected ARIMA and Prophet model are then fitted to the training set and
rolling window forecasts are made 1 day, 30 days and 90 days ahead. This
allows us to examine the forecast horizon effect. The Model Confidence
Set and Mincer-Zarnowitz test is then used to evaluate the forecasts
produced by ARIMA and Prophet against the test set. Since there is no
consensus on which accuracy statistic best measures the performance of
forecasting techniques, the most popular criteria, the Root Mean Squared
Error (RMSE) is employed. The results obtained from the ARIMA model will
be used as a benchmark for comparison. This process is then repeated
based on data which has outliers and missing values present.

@@

This paper makes use of Prophetâs default settings to fit the data,
however weekly seasonality is included in the model. This allows us to
account for our prior knowledge about the closing prices of Bitcoin
which tend to be lower around the weekend however higher mid-week due to
fluctuations in trading activity. Furthermore, a linear trend is
appropriate since Bitcoin does not have an upper limit on its closing
prices.

@@

Rolling window forecasts are useful in evaluating the robustness of a
forecasting method. In a rolling window forecast, the forecasts are made
h-steps at a time and the actual observation rather than the predicted
value is used for the next prediction in the forecast horizon. In this
way, a poor forecast will not have negative consequences on future
forecasts to be made since the observed values will be used to correct
itself for the remaining forecasts (Zhang and Hu 1998). In this paper,
the ARIMA and Prophet model is first fitted to the training set and the
returns are forecasted h-days ahead for h = 1, 30, 90. The size of the
training set is then increased by one observation and the models are
refitted. The next h-day ahead return is forecasted and this process is
repeated until all forecasts have been made into the test set. The h-day
ahead forecasts are then compared to the h-day ahead observed values in
the test set and the forecast errors are calculated to determine the
RMSE.

@@

\[e_R = \arg max_{i}\bigg(\sup_{j\in M}\frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\bigg)\]
\#\# Mincer-Zarnowitz Approach to Forecast Evaluation The
Mincer-Zarnowitz approach to evaluating forecast accuracy is commonly
used and can be useful when comparing the forecasts produced by Prophet
and the ARIMA model. Mincer and Zarnowitz (1969) proposed an absolute
measure to evaluate forecast accuracy that considers the distance
between the actual and predicted values. To analyse the absolute errors
produced by the forecasts, the observed values \(r_t\) are regressed
against the predicted values \(\hat{r_t}\), i.e.
\[r_t = \alpha + \beta\cdot\hat{r_t} + e_t\] where \(\alpha\) represents
the mean distance between the observed and predicted values while
\(\beta\) represents the correlation between the forecasted errors and
predicted values. When \(\alpha = 0\) it implies that the forecasts are
unbiased and do not systematically overestimate or underestimate the
data. When \(\beta = 1\) it implies that the forecasts are efficient and
uncorrelated with the forecasted errors. A joint hypothesis test of
\(H_0: \alpha = 0 \cup \beta = 1\) is performed to check the efficiency
and bias of the forecasts and the model which produces the best results
generates superior forecasts.

@@

The original dataset is modified in order to examine how robust the
ARIMA and Prophet model are when faced with missing values and outliers.
20 values are randomly removed from the training set and 5 outliers are
randomly inserted in place of existing values. Both models are then
fitted to this âdirtyâ dataset and the forecasts are evaluated in
the same way as the ``clean'' dataset.

@@

We notice that a positive intercept and negative slope is still
estimated at the 1 day and 1 month forecast horizon when the data is
dirty. The intercept estimates are larger than the case of the clean
data, suggesting that the biasness of the forecasts yielded by both
models increases when there are outliers and missing values present in
the data. Contrary to the results from the clean data, Prophetâs
intercept estimate lies closer to zero at the 1 month and 3 month
forecast horizon. This indicates that the mean forecasted returns
yielded by Prophet is closer to the mean observed returns when outliers
and missing values are present in the data. The negative intercept and
positive slope estimated for the 3 month horizon contrasts with the
positive intercept and negative slope estimated in the case of the clean
data. This shows that although the forecasts produced by both models are
systematically overestimated at long forecast horizons when the data is
dirty, they are no longer the opposite of the observed returns.

@@

The results show a clear difference in the predictive accuracy of the
ARIMA and Prophet model in addition to the forecast horizon effect. The
ARIMA model ranks ahead of Prophet when forecasting the returns of
BTC/ZAR across all forecast horizons. These results hold true
irrespective of whether there are missing values and outliers present in
the data. Nevertheless, it is reassuring to see that both models have
equal predictive accuracy when forecasting at short and long forecast
horizons when the data is clean and at short forecast horizons when the
data is dirty. Furthermore, the Mincer-Zarnowitz p-values for both
models are significant at the same forecast horizons, suggesting that
the efficiency and biasness of the return forecasts yielded by ARIMA and
Prophet are synchronized at each forecast horizon. Hence, if the analyst
is engaged in short-term or long-term trading, they could choose to
employ the Prophet model instead of the ARIMA model. This would allow
them to produce return forecasts that are as good as the ARIMA model,
without having any expert knowledge about model building and selection.
It would also provide them with the flexibility to customise the model
to suit their needs and incorporate their domain knowledge about BTC/ZAR
through the modelâs intuitively adjustable parameters. If the analyst
is interested in generating unbiased and/or efficient forecasts with the
least amount of forecast error, they could utilise either model, however
should only forecast BTC/ZAR returns over long forecast horizons with
data that do not include any outliers or missing values.

@@

Although the Prophet model was eliminated from the Model Confidence Set
at other forecast horizons, these results might change as more data and
information about events which might impact the price of BTC/ZAR becomes
available and is incorporated into the Prophet model. Furthermore, the
RMSE shows that the difference between the forecast errors of ARIMA and
Prophet is marginal, even in the case where both models donât have
equal predictive accuracy. Hence, if the analyst is willing to sacrifice
a small amount of predictive accuracy in return for the tractability and
ease of implementation which Prophet provides, then they might favour
Prophet over the ARIMA model.

>>>>

The techniques that have been considered for exchange rate forecasting
thus far, require the analyst to have vocational knowledge about time
series. Prophet differs from traditional time series models in that it
is flexible and can be customised by a large number of non-experts who
have little knowledge about time series, however have domain knowledge
about the data generating process. Prophet allows for a large number of
forecasts to be produced across a variety of problems and consists of a
robust evaluation system that allows for a large number of forecasts be
evaluated and compared. This is Facebook's definition of forecasting at
scale.

Prophet's Bayesian approach to forecasting allows the analyst to
incorporate their expert knowledge into the model building process and
has produced significantly improved forecasts compared to the ARIMA
model. Taylor and Letham (2017) forecasted the number of events on
Facebook using Prophet. The time series was impacted by holidays, had
strong multi-period seasonality, and a piecewise trend. The forecasts
produced by Prophet were compared to common forecasting techniques such
as exponential smoothing, ARIMA, the seasonal naive, and the naive
model. While exponential smoothing and the seasonal naive model were
quite robust, the ARIMA forecasts were fragile. No model besides Prophet
accounted for the dips around holidays and the upward trend of the time
series towards later observations. If Prophet produces forecasts that
are as good as the ARIMA model when forecasting BTC/ZAR, it can be
compared to more complex forecasting methods that are less tractable
such as the hybrid models and machine learning techniques seen earlier.

@@

Prophet, like the GAM, frames the forecasting problem as a curve-fitting
exercise and uses backfitting to find the regression functions. This
allows for the model to be fitted quickly and missing values and large
outliers to be handled elegantly. The regression model also provides
model flexibility and allows the analyst to interactively change model
parameters (Taylor and Letham 2017). The growth component of Prophet may
be modelled as a linear or non-linear function of time. Linear growth is
modelled by a piecewise constant function while non-linear growth is
modelled similar to population growths which use a logistic growth model
(Taylor and Letham 2017). A time-varying upper limit may be specified
for logistic growth, at which point the forecasts will saturate. This
carrying capacity allows the analyst to incorporate their prior
knowledge about the maximum obtainable growth level such as the total
market or population size into the model. Prophet accounts for changes
in the trajectory of this trend by automatically detecting and selecting
changepoints in the data at which the growth rate is allowed to change.
These changepoints have a Laplace prior distribution placed on them and
its scale parameter may be used to adjust the flexibility of the trend
and to choose how aggressively the model should follow historical trend
changes. Analysts may also adjust the number of potential changepoints
included or manually specify their location. This allows non-experts
with knowledge about events that may affect the growth rate to use the
parameter as a knob to either increase or decrease the number of
changepoints included (Taylor and Letham 2017). It also allows for the
analyst to add changepoints which the automatic selection procedure may
have missed or remove changepoints when the model is overfitting
historical trends (Taylor and Letham 2017).

@@

Prophet's ability to forecast at scale enables it to model a wide
variety of data and may be able to adequately fit exchange rate data.
Its non-linear components could capture the non-linearity present in
exchange rates. In contrast, the ARIMA model is a linear function of
previous observations and lagged residuals and fails to capture the
non-linearity inherent in exchange rate data. Prophet performs well on
data with strong multiple ``human scale'' seasonalities and historical
trend changes. This differs to the ARIMA model which requires the data
to be de-trended and the variance stabilised before the model can be
fitted. Hence Prophet could model the weekly seasonality of closing
prices due to low trading activity which occurs around the weekend and
high trading activity which occurs mid-week.

@@

In this paper, the out-of-sample forecasts of ARIMA and Prophet are
compared over varying forecast horizons. The data is first split into a
training set and test set. The training set starts on the 24th January
2016 and ends on the 16th January 2017, while the test set starts on the
17th January 2017 and ends on the 17th July 2017. The Box-Jenkins
methodology is then used to select the correct ARIMA model while
Prophet's semi-automatic procedure is used for model selection. The
selected ARIMA and Prophet model are then fitted to the training set and
rolling window forecasts are made 1 day, 30 days and 90 days ahead. This
allows us to examine the forecast horizon effect. The Model Confidence
Set and Mincer-Zarnowitz test is then used to evaluate the forecasts
produced by ARIMA and Prophet against the test set. Since there is no
consensus on which accuracy statistic best measures the performance of
forecasting techniques, the most popular criteria, the Root Mean Squared
Error (RMSE) is employed. The results obtained from the ARIMA model will
be used as a benchmark for comparison. This process is then repeated
based on data which has outliers and missing values present.

@@

This paper makes use of Prophet's default settings to fit the data,
however weekly seasonality is included in the model. This allows us to
account for our prior knowledge about the closing prices of Bitcoin
which tend to be lower around the weekend however higher mid-week due to
fluctuations in trading activity. Furthermore, a linear trend is
appropriate since Bitcoin does not have an upper limit on its closing
prices.

@@

Rolling window forecasts are useful in evaluating the robustness of a
forecasting method. In a rolling window forecast, the forecasts are made
h-steps at a time and the actual observation rather than the predicted
value is used for the next prediction in the forecast horizon. In this
way, a poor forecast will not have negative consequences on future
forecasts to be made since the observed values will be used to correct
itself for the remaining forecasts (Zhang and Hu 1998). In this paper,
the ARIMA and Prophet models are first fitted to the training set and
the returns are forecasted h-days ahead for h = 1, 30, 90. The size of
the training set is then increased by one observation and the models are
refitted. The next h-day ahead return is forecasted and this process is
repeated until all forecasts have been made into the test set. The h-day
ahead forecasts are then compared to the h-day ahead observed values in
the test set and the forecast errors are calculated to determine the
RMSE.

@@

\[e_R = \arg max_{i}\bigg(\sup_{j\in M}\frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\bigg)\]

\subsection{Mincer-Zarnowitz Approach to Forecast
Evaluation}\label{mincer-zarnowitz-approach-to-forecast-evaluation}

The Mincer-Zarnowitz approach to evaluating forecast accuracy is
commonly used and can be useful when comparing the forecasts produced by
Prophet and the ARIMA model. Mincer and Zarnowitz (1969) proposed an
absolute measure to evaluate forecast accuracy that considers the
distance between the actual and predicted values. To analyse the
absolute errors produced by the forecasts, the observed values \(r_t\)
are regressed against the predicted values \(\hat{r_t}\), i.e.
\[r_t = \alpha + \beta\cdot\hat{r_t} + e_t\] where \(\alpha\) represents
the mean distance between the observed and predicted values while
\(\beta\) represents the correlation between the forecasted errors and
predicted values. When \(\alpha = 0\) it implies that the forecasts are
unbiased and do not systematically overestimate or underestimate the
data. When \(\beta = 1\) it implies that the forecasts are efficient and
uncorrelated with the forecasted errors. A joint hypothesis test of
\(H_0: \alpha = 0 \cup \beta = 1\) is performed to check the efficiency
and bias of the forecasts and the model which produces the best results
generates superior forecasts.

@@

The original dataset is modified in order to examine how robust the
ARIMA and Prophet model are when faced with missing values and outliers.
20 values are randomly removed from the training set and 5 outliers are
randomly inserted in place of existing values. Both models are then
fitted to this ``dirty'' dataset and the forecasts are evaluated in the
same way as the ``clean'' dataset.

@@

We notice that a positive intercept and negative slope is still
estimated at the 1 day and 1 month forecast horizon when the data is
dirty. The intercept estimates are larger than the case of the clean
data, suggesting that the biasness of the forecasts yielded by both
models increases when there are outliers and missing values present in
the data. Contrary to the results from the clean data, Prophet's
intercept estimate lies closer to zero at the 1 month and 3 month
forecast horizon. This indicates that the mean forecasted returns
yielded by Prophet is closer to the mean observed returns when outliers
and missing values are present in the data. The negative intercept and
positive slope estimated for the 3 month horizon contrasts with the
positive intercept and negative slope estimated in the case of the clean
data. This shows that although the forecasts produced by both models are
systematically overestimated at long forecast horizons when the data is
dirty, they are no longer the opposite of the observed returns.

@@

The results show a clear difference in the predictive accuracy of the
ARIMA and Prophet model in addition to the forecast horizon effect. The
ARIMA model ranks ahead of Prophet when forecasting the returns of
BTC/ZAR across all forecast horizons. These results hold true
irrespective of whether there are missing values and outliers present in
the data. Nevertheless, it is reassuring to see that both models have
equal predictive accuracy when forecasting at short and long forecast
horizons when the data is clean and at short forecast horizons when the
data is dirty. Furthermore, the Mincer-Zarnowitz p-values for both
models are significant at the same forecast horizons, suggesting that
the efficiency and biasness of the return forecasts yielded by ARIMA and
Prophet are synchronized at each forecast horizon. Hence, if the analyst
is engaged in short-term or long-term trading, they could choose to
employ the Prophet model instead of the ARIMA model. This would allow
them to produce return forecasts that are as good as the ARIMA model,
without having any expert knowledge about model building and selection.
It would also provide them with the flexibility to customise the model
to suit their needs and incorporate their domain knowledge about BTC/ZAR
through the model's intuitively adjustable parameters. If the analyst is
interested in generating unbiased and/or efficient forecasts with the
least amount of forecast error, they could utilise either model, however
should only forecast BTC/ZAR returns over long forecast horizons with
data that do not include any outliers or missing values.

@@

Although the Prophet model was eliminated from the Model Confidence Set
at other forecast horizons, these results might change as more data and
information about events which might impact the price of BTC/ZAR becomes
available and is incorporated into the Prophet model. Furthermore, the
RMSE shows that the difference between the forecast errors of ARIMA and
Prophet is marginal, even in the case where both models don't have equal
predictive accuracy. Hence, if the analyst is willing to sacrifice a
small amount of predictive accuracy in return for the tractability and
ease of implementation which Prophet provides, then they might favour
Prophet over the ARIMA model.
